No-click browsing of large hierarchical data

### 2020-03-07 paper/HCC2020/paper.tex
...

We can use no-click browsing on old TVs and radios because the number of
broadcast channels are limited.
Likewise, we can use no-click browsing on Finder.app when the number of files
in a folder is not very large.

No-click browsing is not popular on conventional GUI of personal computers.
People are used to click-based browsing on web browsers and other
information visualization systems.
People can navigate through a huge information space by
clicking links, zooming by dragging, and using other GUI techniques.
These techniques are useful for finding an item in a large information space,
but many clicks and drag operations are required.
The contents of the items are usually not shown during the search.

@@

\begin{figure}[H]
% \centerline{\includegraphics[width=80mm,bb=0 0 524 598]{figures/65b01a87b67c9a8e838a047b945f6a77.png}}
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
\caption{Showing ``Breakfast at Tiffany's''.}
\label{tiffany}
\end{figure}

@@

One of the authors have been using Gear in his living room for several years
with a small personal computer connected to a 60-inch TV monitor.
The database is managed on {\SB}, and
a mouse wheel of a wireless Bluetooth mouse is used for Gear interface.
With Gear, the user can enjoy all available contents on the web with the mouse wheel
without selecting the source of the movies, animes, and musics (e.g. Amazon, Netflix, etc.).

>>>>

We can use no-click browsing on old TVs and radios because the number of
broadcast channels are limited.
Likewise, no-click browsing on Finder.app is useful
when the number of files in a folder is not very large.

No-click browsing is not popular on conventional GUI of personal computers.
People are used to click-based browsing on web browsers and other
information visualization systems.
People can navigate through a huge information space by
clicking links, zooming by dragging, and using other GUI techniques.
These techniques are useful for finding an item in a large information space,
but many clicks and drag operations are required,
and the contents of the items are usually not shown during the search.

@@

\begin{figure}[H]
% \centerline{\includegraphics[width=80mm,bb=0 0 524 598]{figures/65b01a87b67c9a8e838a047b945f6a77.png}}
\centerline{\includegraphics[width=80mm,bb=0 0 2400 1600]{figures/e8ae562a5a68a1955ac70b4faed9a146.png}}
\caption{Watching ``Breakfast at Tiffany's''.}
\label{tiffany}
\end{figure}

@@

One of the authors have been using Gear in his living room for several years
with a small personal computer connected to a 60-inch TV monitor.
The database is managed on {\SB}, and
a mouse wheel of a wireless Bluetooth mouse is used for Gear interface.
With Gear, the user can enjoy all available contents on the web with the mouse wheel
without selecting the source of the movies, animes, and musics from Amazon, Netflix, etc.
